### 2022-06-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@d4a5cee100420e126780c4c1afe18f7b5484f993 🚀

(\textbf{Torres2020GleGeo?})\strut

@@

(\textbf{S2013GraEmb?})\strut

@@

@@

\leavevmode\hypertarget{ref-Stevenson2021AlgRis}{}%
Stevenson, M. T., \& Doleac, J. L. (2021). \emph{Algorithmic Risk
Assessment in the Hands of Humans} {[}SSRN Scholarly Paper{]}.
\url{https://doi.org/10.2139/ssrn.3489440}

@@

>>>>

Torres et al. (2020)\strut

@@

S \& Surendran (2013)\strut

@@

\leavevmode\hypertarget{ref-S2013GraEmb}{}%
S, N. S., \& Surendran, S. (2013). Graph Embedding and Dimensionality
Reduction - A Survey. \emph{International Journal of Computer Science \&
Engineering Technology}, \emph{4}(1).
\url{https://www.semanticscholar.org/paper/Graph-Embedding-and-Dimensionality-Reduction-A-Surendran/3f413d591e4b2b876e033eeb9390e232ad4826ca}

@@

\leavevmode\hypertarget{ref-Stevenson2021AlgRis}{}%
Stevenson, M. T., \& Doleac, J. L. (2021). \emph{Algorithmic Risk
Assessment in the Hands of Humans} (SSRN Scholarly Paper No. 3489440).
\url{https://doi.org/10.2139/ssrn.3489440}

@@

\leavevmode\hypertarget{ref-Torres2020GleGeo}{}%
Torres, L., Chan, K. S., \& Eliassi-Rad, T. (2020). GLEE: Geometric
Laplacian Eigenmap Embedding. \emph{Journal of Complex Networks},
\emph{8}(2), cnaa007. \url{https://doi.org/10.1093/comnet/cnaa007}
